A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-04-22 report_clean/FD.tex
one more alpha

\begin{remark} 
\label{remark:other}
The above proof is not optimal in the case when $\left|\alpha(x)\right|>c>0$ for $c>0$ on the whole interval $[-L,\; H]$, at least 
for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
with the variable coefficient $k^2=(\alpha(x)-\frac{\delta^2}{\alpha})$, and the second equation 
\begin{align*}
  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha(x)}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
\end{align*}
uniquely defines $E_x\in L^{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the second equation.

>>>>

\begin{remark} 
\label{remark:other}
The above proof is not optimal in the case when $\left|\alpha(x)\right|>c>0$ for $c>0$ on the whole interval $[-L,\; H]$, at least 
for the case $\theta=0$. In this case the problem (\ref{eq:var_form2}) is well-posed for $\nu=0$. More precisely, it can be written 
as a system of two equations, where the first equation (for $E_y$) is the variational formulation for the Helmholtz equation 
with the variable coefficient $k^2=(\alpha(x)-\frac{\delta^2}{\alpha(x)})$, and the second equation 
\begin{align*}
  \left(E_x,u\right)=-\left(\frac{i\delta}{\alpha(x)}E_y,u\right),\; \text{ for all } u\in L^{2}(\Omega), 
\end{align*}
uniquely defines $E_x\in L^{2}(\Omega)$. The well-posedness of the former problem, with additional assumptions on boundary conditions and smoothness of the coefficients, 
was demonstrated in \cite{LMIG_thesis}. Provided the solution $E_y\in H^{1}(\Omega)$, we can obtain $E_x$ from the second equation.
